\documentclass[10pt,letter]{moderncv}
\usepackage[utf8]{inputenc}
\moderncvtheme[blue]{classic}

\firstname{Austin}
\familyname{Redmond}
\address{}{T5T 2E3 Edmonton, AB}
\mobile{+1~(780)~200~8723}
\phone{+2~(780)~487~4106}
\email{austinredmond@protonmail.com}

\begin{document}
\makecvtitle

\section{Education}

\cventry{2018-2020}{Bachelor of Science}{MacEwan University}{}{}{ %
	Majored in Applied Statistics with Finance Minor.\\
	Completed the Tri-Council Policy Statement: Ethical Conduct for Research Involving Humans Course on Research Ethics.\\
	Competed in the 2019 Canadian Statistical Sciences Institute National Case Study Competition.}

\cventry{2013-2017}{Bachelor of Arts}{University of Alberta}{}{}{ %
	Majored in Economics with Computing Science Minor.\\
	Competed in the 2016 Bank of Canada - Governor's Challenge.}

\cventry{2010-2013}{High School Diploma}{Jasper Place School}{Edmonton, AB}{}{}

\section{Work Experience}

\cventry{2018-Present}{Merchandiser}{Excel Foods Inc.}{Edmonton, AB}{}{ % 
	Stock and rotate Canada Bread products on store shelves and displays.\\
	Work with minimal supervision.
}

\cventry{2017}{Enviro}{Mash Marketing Inc.}{}{}{ %
	Removed promotional materials from LRT cars for recycling.\\
	Worked without on-site supervision.}

\cventry{2013-2015}{Promoter}{Mash Marketing Inc.}{}{}{ %
	Distributed promotional materials on the daily early mornings team.\\
	Interacted with thousands of members of the public every shift.\\
	Worked without on-site supervision.}

\section{Volunteer Experience}

\cventry{2013-Present}{Debate Coach}{Westminster School}{Edmonton, AB}{}{ % 
	Develop and deliver debate curriculum for students aged 12-14.\\
	Organize debate events including workshops and tournaments.\\	
	Evaluate and address student skill sets.}

\cventry{2020-Present}{Edmonton Junior High Debate Representative}{Alberta Debate and Speech Association}{}{}{ % 
	Provide liaison between debate clubs, coaches, and the board.\\
	Support new and existing coaches in the community.\\
	Create materials to aide in the transition to online debate tournaments.}

\cventry{2015-2017}{Northern Alberta Alumni Representative}{Alberta Debate and Speech Association}{}{}{ % 
	Coordinated university-level debaters who coached jr/sr debate clubs.\\
	Created topics and prepared research packages for students.\\
	Created the draw and tracked statistics for debate tournaments.\\
	Awarded the 2016 John Baty Award for the "Adult or Association that makes the most outstanding contribution to debate".}

\section{Skills}

\cvline{\footnotesize Knowledge}{As a finance minor I familiarized myself with EI and CPP premiums from a tax perspective.}
\cvline{\footnotesize Communication}{As a competitor in case studies I communicated findings from my analysis to judges.}
\cvline{\footnotesize Customer Service}{As a promoter I dealt with thousands of people and helped many with directions to places near my jobsite.}
\cvline{\footnotesize Thinking}{As a student I studied a breadth of disciplines over several faculties in arts, sciences, and business.}
\cvline{\footnotesize Information Gathering}{As an applied statistics major I gathered information for various research projects.}
\cvline{\footnotesize Data Entry}{As the Northern Alberta Alumni Representative I gathered participant information and competitor scores into software for debate tournaments.}
\cvline{\footnotesize Passion for Helping Others}{As a debate coach I volunteered to help students develop their debate skills.}
\cvline{\footnotesize Technology Usage}{As the Edmonton Junior High Debate Representative I use e-mail, the Internet and word processing to communicate with the board and other coaches.}
\cvline{\footnotesize Delivering Services/Programs}{As the Edmonton Junior High Debate Representative I have hosted seminars teaching coaches how to use technology for online debate tournaments.}
\cvline{\footnotesize Language}{As a student my oral and written assessments have been in English.}

\end{document}